% text document formatting

\documentclass[11pt]{article}
\usepackage{hyperref}

%\title{My LaTeX Document}
%\title{My \LaTeX Document}
\title{My \LaTeX\ Document}
\author{Md. Zahangir Alam}
%\date{July 17 2023}
\date{\today}

\begin{document}
\tableofcontents
\maketitle

this is will produces \textit{italicized} text.

this is will produces \textbf{bold face} text.

this is will produces \textsc{small caps} text.

this is will produces \texttt{typewriter} text.

Please visit CS website at \texttt{http://cs.joy.com}.

Please visit CS website at \url{https://github.com}.

Please visit CS website at \href{https://github.com}{Github}.

\vspace{1cm}
Good day to You.

Good day \begin{large}to You\end{large}.

Good day \begin{Large}to You\end{Large}.

Good day \begin{huge}to you\end{huge}.

Good day \begin{Huge}to you\end{Huge}.


Good day \begin{normalsize}to You\end{normalsize}.


Good day \begin{small}to You\end{small}.

Good day \begin{scriptsize}to You\end{scriptsize}.

Good day \begin{tiny}to You\end{tiny}.


\vspace{1cm}
\begin{center}text position center.\end{center}

\begin{flushleft}text position left-justified.\end{flushleft}

\begin{flushright}text position right-justified.\end{flushright}

%\centering
%this line is center.\\
%this line is left-justified.\\
%this line is right-justified.

%\Large
%this line is center.

%this line is left-justified.

%this line is right-justified.

\tiny
this line is center.

this line is left-justified.

this line is right-justified.


\section{Linear Functions}
	\subsection{Slope-intercept form}
		\subsubsection{Example 1:}
		\subsubsection{Example 2:}
	\subsection{Standard form}
		\subsubsection*{Example 1:} %removed number - infron of title
		\subsubsection*{Example 2:}	
	\subsection{Point-slope form}
\section{Quadratic Functions}
	\subsection{Vertex form}
	\subsection{Standard form}
	\subsection{Factored form}










\end{document}